Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Prefix figures with "meek-".

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as a pluggable transport~\cite{pt} for Tor.
\meek combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received by the server from Tor
are returned to the client within HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{architecture}
\caption{
Architecture of \meek.
The client sends an HTTP request to the Tor bridge by way of an intermediate web service such as a CDN.
The client protects the bridge's domain name \textbf{forbidden.example} from the censor
by fronting it with another name, here \textbf{allowed.example}.
The intermediate web server decrypts the TLS layer and forwards the request to the bridge
according to the Host header.
The bridge sends data back to the client in the HTTP response.
\meekclient and \meekserver are transport plugins, the interface between Tor and \meek.
The host actually at allowed.example does not participate in the communication.
}
\label{fig:architecture}
\end{figure*}

@@

We show the components of the system in Figure~\ref{fig:architecture}.
The parts that are new in \meek
are the programs \meekclient and \meekserver,
\vp{It would help to use a different typeface for \meekserver, etc.}
which are \meek's interface with Tor.

@@

\begin{figure}
\centering
\includegraphics[height=1.5in]{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless browser runs in the background and is invisible to the user.
This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the client's computer.
The local Tor process runs a helper process that starts both \meekclient
and the headless browser,
then configures \meekclient to proxy its requests through the browser extension.
The user's browser proxies through Tor;
Tor proxies through \meekclient;
and \meekclient proxies through the headless browser.
The headless browser is the only part that ever actually touches the network.
It should be emphasized that the URLs requested by the headless browser extension
have no relation to the URLs the user browses;
the extension only ever makes requests to the front domain.

>>>>

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as a pluggable transport~\cite{pt} for Tor.
\meek combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received by the server from Tor
are returned to the client within HTTP responses.
\meek's architecture appears in Figure~\ref{fig:meek-architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{meek-architecture}
\caption{
Architecture of \meek.
The client sends an HTTP request to the Tor bridge by way of an intermediate web service such as a CDN.
The client protects the bridge's domain name \textbf{forbidden.example} from the censor
by fronting it with another name, here \textbf{allowed.example}.
The intermediate web server decrypts the TLS layer and forwards the request to the bridge
according to the Host header.
The bridge sends data back to the client in the HTTP response.
\meekclient and \meekserver are transport plugins, the interface between Tor and \meek.
The host actually at allowed.example does not participate in the communication.
}
\label{fig:meek-architecture}
\end{figure*}

@@

We show the components of the system in Figure~\ref{fig:meek-architecture}.
The parts that are new in \meek
are the programs \meekclient and \meekserver,
\vp{It would help to use a different typeface for \meekserver, etc.}
which are \meek's interface with Tor.

@@

\begin{figure}
\centering
\includegraphics[height=1.5in]{meek-browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless browser runs in the background and is invisible to the user.
This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:meek-architecture}.
}
\label{fig:meek-browser-architecture}
\end{figure}

Figure~\ref{fig:meek-browser-architecture} shows the interaction of components
on the client's computer.
The local Tor process runs a helper process that starts both \meekclient
and the headless browser,
then configures \meekclient to proxy its requests through the browser extension.
The user's browser proxies through Tor;
Tor proxies through \meekclient;
and \meekclient proxies through the headless browser.
The headless browser is the only part that ever actually touches the network.
It should be emphasized that the URLs requested by the headless browser extension
have no relation to the URLs the user browses;
the extension only ever makes requests to the front domain.
